### 2016-05-05 sec1_introduction.tex
Stage 1
First Draft 0.1

\section{Introduction}
The prevalence of positioning devices has drastically boosted the scale of trajectory data collection. 
Instances include telemetry chips for animal herding histories, 
GPS devices for urban transportation and wearable devices for personal moving activities. 
These positional data are timestamped and can be viewed as trajectories. 
Data analysis on large-scale trajectories benefits a wide range of applications and services, including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, and social recommendations~\cite{bao2013survey}, just to name a few.% CITATIONS FOR THE ABOVE APPLICATIONS.

An important task of data analysis on trajectories is to discover co-moving objects. 
As its name suggests, a \emph{co-movement} pattern~\cite{li2013managing} consists 
of a group of objects that travel together for some duration, where the group is formed
by certain clustering methods. A pattern is prominent 
if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$
are user specified parameters. Depends on further constraints on object clustering
and time duration, several specific patterns are proposed in the literature.

Specifically, on the aspect of object clustering, \emph{flock}~\cite{gudmundsson2006flock} and \emph{group}~\cite{wang2006grouppattern} patterns require objects to be within a disk region.
In contrast, \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} and
\emph{platoon}~\cite{li2015platoon} patterns require objects to be densely connected. 
In terms of the constraints on time duration, \emph{flock}~\cite{gudmundsson2006flock} and \emph{convoy}~\cite{jeung2008convoy}
require the timestamps to be consecutive. \emph{Swarm}~\cite{li2010swarm}, on the
other hand, do not impose any restrictions. \emph{Group}~\cite{wang2006grouppattern} 
and \emph{platoon}~\cite{li2015platoon} introduce the parameter $L$ to control the minimum length of the local-consecutive
timestamps. 
The compare and contrast of these co-movement patterns are presented in Table~\ref{tbl:existing_co_patterns}.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
Pattern & Clustering Method & Consecutiveness on Duration \\ 
\hline 
Flock~\cite{gudmundsson2004flock} & Disk region &  Consecutive \\ 
\hline 
Convoy~\cite{jeung2008convoy} & Density &   Consecutive \\ 
\hline 
Group~\cite{wang2006grouppattern} & Disk region &  Local consecutive $\geq L$ \\ 
\hline 
Swarm~\cite{li2010swarm} & Density  & No constraint \\ 
\hline 
Platoon~\cite{li2015platoon} & Density &  Local consecutive $\geq L$ \\ 
\hline 
\end{tabular} 
\caption{Existing Co-movement Patterns}
\label{tbl:existing_co_patterns}
\end{table}

%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
% 
%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. 
%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. 
%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.

%We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.
We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of five trajectories.
First, the temporal domain is discretized into five snapshots. 
In each snapshot, the objects are clustered as shown in the dotted circle.
By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
the same constraints on the time duration. 
\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
If further set $M=2,K=3$, two \emph{platoon} patterns are found. It is observable that the pattern $\langle\{O_5,O_6\}\{1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e. $\{1\}$) is less than $2$. However, $\langle\{O_5,O_6\}\{1,4,5\} \rangle$ can be reduced to $\langle\{O_5,O_6\}\{4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.

@@

\begin{figure} [h]
\center
\includegraphics[width=0.5\textwidth]{related_work.eps}
\caption{Trajectories and Co-Movement Patterns}
\label{fig:related_work}
\end{figure}

@@

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. Hence, there is an urgent demand for a general platform to support all these co-movement patterns. Another issue with existing methods is that they are built on top of centralized indexes that are not scalable. The maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect millions of trajectories. We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}. The results show that their performance degrades dramatically as the dataset size scales up. None of them can handle millions of trajectories efficiently.

Therefore, our primary contributions in this paper are to close these two gaps. First, we propose a general co-movement pattern definition to incorporate all the related variants in the existing literature. We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem. This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other. Such a pattern is likely to be induced by periodic movements of unrelated objects thus is of low interests. To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$. By so doing, we gain a fine-grained control over the pattern duration, which alleviates the \emph{loose connection} problem. Meanwhile, the general co-movement pattern does not concede its expressiveness. As we show in later sections, the general co-movement pattern is able to reduce to existing patterns by setting appropriate parameters.

Second, we propose a parallel solution based on Spark for scalable pattern mining. Our
solution is a three-step MapReduce alike approach. First, trajectories are partitioned
into snapshots where clusters from each snapshots are formed in parallel. Second, 
clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
are mined from each group. The challenge here is to ensure that
the patterns mined at step three is complete. If not, further shuffles and computations are required which 
significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
shuffle amount at each stage to a minimum, 
we design a novel star-based partition scheme to efficiently partition objects based on their
belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
largely improve the system performance.

@@

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining; Section~\ref{sec:definition} forms the definition of the general co-movement pattern mining; Section~\ref{sec:system_overview} presents our parallel architecture; The solution of mining the general co-movement pattern mining is presented in Section~\ref{sec:solution} and Section~\ref{sec:optimization} discuss various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to showcase the usefulness and efficiency of our system and finally Section~\ref{sec:conclusion} concludes our paper.

>>>>

\section{Introduction}
The prevalence of positioning devices has drastically boosted 
the scale and spectrum of trajectory collection to an unprecedented level. 
Tremendous amounts of trajectories, in the form of sequenced spatial-temporal 
records, are continually generated from animal telemetry chips, 
vehicle GPSs and wearable devices. Data analysis on large-scale 
trajectories benefits a wide range of applications and services, 
including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, and social recommendations~\cite{bao2013survey}, to name just a few.

A crucial task of data analysis on top of trajectories is 
to discover co-moving patterns. A \emph{co-movement} pattern~\cite{li2013managing} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined according to spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
and driven by different mining applications, there are a bunch of variants 
of co-moving patterns that have been developed with more advanced constraints.

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
with different constraints in the attributes of clustering method and length of temporal duration. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} 
and \emph{platoon}~\cite{li2015platoon} patterns adopt density-based 
spatial clustering in determining groups. 
In the temporal dimension, \emph{flock}~\cite{gudmundsson2006flock} 
and \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which was referred to as \emph{global consecutiveness}; 
whereas \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and \emph{platoon}~\cite{li2015platoon} use a compromised manner and allow gaps between the consecutive segments, which was referred to as \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

@@

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||T|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||T|)$\\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|T|)$ \\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$  \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$\\ 
\hline 
\end{tabular} 
\caption{Existing co-movement patterns. The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the size of object, $|T|$ is the maximum size of timestamps among all trajectories.}
\label{tbl:existing_co_patterns}
\end{table}

%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
% 
%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. 
%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. 
%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
clusters of objects in each snapshots are denoted using dotted circles.}
\label{fig:related_work}
\end{figure}

%%We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.
%UPDATE THE FIGURE TO CONTAIN SIX SNAPSHOTS. USE A NEW REPRESENTATION OF THE PATTERN. I DON'T LIKE $\{o_1,o_2\}\{1,2,3\}$. USE ONE PAIR OF $\{\}$ ONLY.

We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
The temporal dimension is discretized into six snapshots. 
In each snapshot, the objects are clustered as shown in the dotted circle.
By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
the same constraints on the time duration. 
\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
If further set $M=2,K=3$, two \emph{platoon} patterns are found. It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e. $\{1\}$) is less than $2$. However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.

@@

@@

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. Hence, there is a particular demand for a general platform to support all these co-movement patterns. The other issue with existing methods is that they are built on top of centralized indexes that are not scalable. To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown. We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}. The results show that their performance degrades dramatically as the dataset size scales up. In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity. For instance, the
complexities of \emph{swarm} and \emph{platoon} are already exponential. 
Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.

Therefore, our primary contributions in this paper are to close these two gaps. First, we propose a general co-movement pattern definition to incorporate all the related variants in the existing literature. We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem. 
The \emph{loose connection} problem refers to the patterns that discovered 
are loosely-connected in the temporal domain. For example, in Figure~\ref{fig:platoon_weakpoint}, two objects $o_1, o_2$ 
would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
duration is $98$ timestamps apart, making the co-movement behavior very weak.
%
%
%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$. By so doing, we gain a fine-grained control over the pattern duration, which alleviates the \emph{loose connection} problem. Meanwhile, the general co-movement pattern does not concede its expressiveness. As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. 
%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?

%
\begin{figure}[h]
\center
\includegraphics[width=0.45\textwidth]{platoon_weakpoint.eps}
\caption{Loosely connected pattern in platoon and swarm. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
\label{fig:platoon_weakpoint}
\end{figure}

Second, we propose a parallel solution based on modern MapReduce platform for scalable pattern mining. Our
solution is a three-step MapReduce alike approach. First, trajectories are partitioned
into snapshots where clusters from each snapshots are formed in parallel. Second, 
clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
are mined from each group. The challenge here is to ensure that
the patterns mined at step three is complete. If not, further shuffles and computations are required which 
significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
shuffle amount at each stage to a minimum, 
we design a novel star-based partition scheme to efficiently partition objects based on their
belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!

@@

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining; Section~\ref{sec:definition} forms the definition of the general co-movement pattern mining; Section~\ref{sec:system_overview} presents our parallel architecture; The solution of mining the general co-movement pattern mining is presented in Section~\ref{sec:trm_solution} and Section~\ref{sec:spm_solution}. Section~\ref{sec:optimization} discuss various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to showcase the usefulness and efficiency of our system and finally Section~\ref{sec:conclusion} concludes our paper.

### 2016-05-05 sec3_definitions.tex
Stage 1
First Draft 0.1

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern. 
We use $T \subseteq \{1,2,...,m\}$ to denote a descritized sequence of timestamps, where
$T[i]$ denotes the $i^{th}$ entry in the sequence and $|T|$ is the 
cardinality of the sequence.

A time sequence is consecutive if the difference between any of its neighboring entries
is 1, that is $\forall T[i], T[i+1] \in T, T[i+1] = T[i] + 1$. For any time sequence,
it can be decomposed into at least one consecutive portion(s). Therefore we can define the 
$L$-consecutiveness as follows:
%
%
%We say a sequence $T$ is \emph{(fully)consecutive}
%if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $L$-consecutiveness as follows:

\begin{definition}[$L$-consecutive~\cite{li2015platoon}]
A time sequence $T$ is $L$-consecutive if each of its consecutive portions 
has cardinality greater or equal to $L$.
\end{definition}

Take $T=\{1,2,3,5,6\}$ as an example. $T$ is not $3$-consecutive since $\{5,6\}$ has a cardinality less than $3$. $T$ is $2$-consecutive since both of its consecutive portions are of sizes at least $2$.
To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows:

@@

Take $T=\{1,2,3,5,6\}$ as an example. $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$. However, $T$ is not $1$-connected. Indeed, $1$-connection infers that $T$ is consecutive.

Given a timestamp $t$, objects with their locations at $t$ collectively form a \emph{snapshot}\footnote{Missing time stamps can be interpreted using existing methods such as linear interpolation~\cite{jeung2008convoy}.}.Objects in a snapshot can then be clustered based on the
closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, a general co-movement pattern can be defined as:
\begin{definition}[General Co-Movement Pattern]
A \emph{General co-movement pattern} $GCMP(M,K,L,G)= \langle O,T \rangle$ is a pair containing an object set $O\subseteq \mathbb{O}$ and a time sequence $T$, with the following constraints: (1)Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$. (2) Significance: $|O| \geq M$. (3) Duration: $|T| \geq K$. (4) Consecutiveness: $T$ is $L$-consecutive, and (5)Connection: $T$ is $G$-connected.
%\begin{enumerate}
%\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
%\item{Significance: $|O| \geq M$}
%\item{Duration: $|T| \geq K$}
%\item{Consecutiveness: $T$ is $L$-consecutive}
%\item{Separateness: $T$ is $G$-separated}
%\end{enumerate} 
\end{definition}

The general co-movement pattern retains the patterns that discovered by all 
existing techniques (group, flock, convoy, swarm and platoon). 
The relationships between general co-movement pattern and other patterns are summarized in Table~\ref{tbl:patterns}.
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Pattern & $L$ & $G$ & $M$ & $K$ \\ 
\hline
Group & $\cdot$ & $|T|$ & $2$ & $1$ \\
\hline
Flock & $K$ & 1 & $\cdot$ & $\cdot$ \\
\hline 
Convoy & $K$ & $1$ & $\cdot$ & $\cdot$\\ 
\hline 
Swarm & $1$ & $|T|$ & $\cdot$ & $\cdot$ \\ 
\hline 
Platoon & $\cdot$ & $|T|$ & $\cdot$ & $\cdot$\\ 
\hline 
\end{tabular} 
\caption{Representing other patterns using GCMP. $\cdot$ means user specified value.}
\label{tbl:patterns}
\end{table}

In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern. By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern. 
In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern. As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent. By setting appropriate $G$, we are able to prune this anomaly. It is notable that GCMP is not able to be modeled by existing patterns.

@@

LETS KEEP THE CLOSENESS INFORMATION AT THE MOMENT. IF NO CLOSENESS IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.

%Although the general co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting object clusters with arbitrary spatio-shapes. Therefore in this paper, we mainly consider density-based clustering.
Our definition of GCMP is free from clustering method. Users are able to supply different clustering method to facilitate different needs. We currently expose both disk-region based clustering and DBSCAN as APIs to the user.

>>>>

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =\{1,2,...,m\}$ be the descritized temporal dimension. A time sequence $T$ is defined as a subset of $\mathbb{T}$, i.e., $T \subseteq \mathbb{T}$, and we use $|T|$ to denote sequence length. Let $T_i$ be $i$-th entry in $T$ and we say $T$ is consecutive if $\forall 1\leq i\leq |T|-1$, $T_{i+1} = T_i + 1$. It is obvious that any time sequence $T$ can be decomposed into consecutive segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} if the length of all the consecutive segments is no smaller than $L$.

To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows: WHAT THE RELATIONSHIP BETWEEN CLOSENESS AND G-CONNECTED?

%
%
%We say a sequence $T$ is \emph{(fully)consecutive}
%if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $L$-consecutiveness as follows:

%\begin{definition}[$L$-consecutive~\cite{li2015platoon}]
%A time sequence $T$ is $L$-consecutive if each of its consecutive portions 
%has cardinality greater or equal to $L$.
%\end{definition}

@@

We take $T=\{1,2,3,5,6\}$ as an example, which can be decomposed into two consecutive segments $\{1,2,3\}$ and $\{5,6\}$. $T$ is not $3$-consecutive since the length $\{5,6\}$ is $2$. Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$. It is worth noting that $T$ is not $1$-connected because XXX.

%Given a timestamp $t$, objects with their locations at $t$ collectively form a \emph{snapshot}\footnote{Missing time stamps can be interpreted using existing methods such as linear interpolation~\cite{jeung2008convoy}.}.Objects in a snapshot can then be clustered based on the closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, a general co-movement pattern can be defined as:
Given a trajectory database descritized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: 1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; 2) \textit{significance:} $|O| \geq M$; 3) \textit{duration:} $|T| \geq K$; 4) \textit{consecutiveness:} $T$ is L-consecutive; and 5) \textit{connection:} $T$ is $G$-connected.

%\begin{enumerate}
%\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
%\item{Significance: $|O| \geq M$}
%\item{Duration: $|T| \geq K$}
%\item{Consecutiveness: $T$ is $L$-consecutive}
%\item{Separateness: $T$ is $G$-separated}
%\end{enumerate} 
\end{definition}
There are XXX parameters in our general co-movement pattern, including XXX. By customizing these parameters, our pattern can be reduced to the patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern. By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern. 
In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern. As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent. By setting appropriate $G$, we are able to prune this anomaly. It is notable that GCMP is not able to be modeled by existing patterns. AS MENTIONED IN WECHAT, POLISH THIS PART.

%The general co-movement pattern retains the patterns that discovered by all 
%existing techniques (group, flock, convoy, swarm and platoon). 
%The relationships between general co-movement pattern and other patterns are summarized 
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Pattern & $L$ & $G$ & $M$ & $K$ \\ 
\hline
Group & $\cdot$ & $|T|$ & $2$ & $1$ \\
\hline
Flock & $K$ & 1 & $\cdot$ & $\cdot$ \\
\hline 
Convoy & $K$ & $1$ & $\cdot$ & $\cdot$\\ 
\hline 
Swarm & $1$ & $|T|$ & $\cdot$ & $\cdot$ \\ 
\hline 
Platoon & $\cdot$ & $|T|$ & $\cdot$ & $\cdot$\\ 
\hline 
\end{tabular} 
\caption{Representing other patterns using GCMP. $\cdot$ means user specified value.}
\label{tbl:patterns}
\end{table}

@@

LETS KEEP THE CLOSED INFORMATION AT THE MOMENT. IF NO CLOSED IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.

%Although the general co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting object clusters with arbitrary spatio-shapes. Therefore in this paper, we mainly consider density-based clustering.
Our definition of GCMP is free from clustering method. Users are able to supply different clustering method to facilitate different needs. We currently expose both disk-region based clustering and DBSCAN as options to the user.
